A Database Management System for a Geospatially-Enabled Interactive Game

### 2018-12-08 paper/MSDS7330DBMSforGeospatiallyEnabledGame - Copy.tex
Referenced the Figure

The story is a science fiction story that places the player in the role of an explorer. The player finds himself exploring ruins on another world that once housed an advanced civilization. The player must then find objects that will divulge information about this lost civilization including clues as to what caused the civilization to disappear. Categories consist of Culture, Politics, and Technology and correspond to the nature of the clues the player discovers. For example, culture objects reveal how the civilization lived and what cultural tensions were present before they disappeared.

>>>>

The story is a science fiction story that places the player in the role of an explorer. The player finds himself exploring ruins on another world that once housed an advanced civilization and is charged with learning how the beings lived and what caused their disappearance. The player must then find objects, divided into three categories, that will divulge the necessary information about how this lost civilization lived and why it disappeared. Categories consist of Culture, Politics, and Technology and correspond to the nature of the player’s discoveries and tell the story of the civilization in tandem. For example, culture objects reveal how the civilization lived and what cultural tensions were present before they disappeared. Furthermore, the story arc of the civilization’s culture is told independently of the technology and politics story arcs, but with the common overarching plot of the civilization’s demise. An illustration of the story arc concept is presented below in \autoref{Tandem}.

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{imgs/TandemPlot2.png}
\caption{Illustration of Tandem Story Arcs}
\label{Tandem}
\end{figure}
